%-------------------------
% Author : Turan Naimey
% Source: https://github.com/turanoo/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Enable ATS parseability
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & \textit{\small #4} \\
      \textit{\small#5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




% Document begins here
\begin{document}

\begin{center}
 \textbf{\Huge \scshape Turan Naimey} \\ \vspace{1pt}
 \small 347-852-6534 $|$ \href{mailto:turan1naimey@gmail.com}{\underline{turan1naimey@gmail.com}} $|$
 \href{https://linkedin.com/in/turannaimey}{\underline{linkedin.com/in/turannaimey}} $|$
 \href{https://github.com/turanoo}{\underline{github.com/turanoo}}
\end{center}

% List your employment under this section
\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
{Cigna Digital}{March 2023 -- Present}
{Senior Software Engineer}{Remote}
{Evernorth - Backend Engineer}
\resumeItemListStart
\resumeItem{Architected and implemented a centralized onboarding module using \textbf{Golang}, integrating \textbf{Auth0} for authentication and authorization and \textbf{AWS Lambda} for serverless workflows.}
\resumeItem{Developed an end-to-end Consent Management Platform integrating \textbf{OneTrust}, \textbf{AWS}, \textbf{Kafka} to ensure compliance with \textbf{HIPAA} and \textbf{GDPR}, streamlining user consent tracking and data privacy enforcement.}
\resumeItem{Designed and implemented a Customer-Profile API leveraging \textbf{Golang}, \textbf{GraphQL}, \textbf{ElastiCache}, \textbf{OpenSearch}, \textbf{SQS} and \textbf{EventBridge},   improving data retrieval efficiency and reducing latency by 40\%. }
\resumeItem{Developed a scalable Entitlements API deployed on \textbf{EKS}, integrating with \textbf{LaunchDarkly} to enable controlled feature rollout.}
\resumeItem{Utilized \textbf{Terraform} to build and manage infrastructure, \textbf{GitLab CI/CD pipelines} for continuous integration and deployment, and \textbf{Splunk} for monitoring and telemetry, ensuring efficient operations and proactive issue detection.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\resumeSubHeadingListStart
\resumeSubheading
{Tanium}{August 2021 -- December 2022}
{Software Engineer}{Remote}
{IT \& Cybersecurity Operations - Backend Engineer}
\resumeItemListStart
\resumeItem{Utilized \textbf{Node}, \textbf{Python}, and \textbf{Golang} to enhance Patch and Deploy solutions securing over 28 million endpoints.}
\resumeItem{Created a robust dependency management system using \textbf{Flask} and  to comply with federal security guidelines.}
\resumeItem{Revamped \textbf{CI/CD pipeline} from \textbf{Jenkins} to \textbf{GitHub Actions}, reducing build times from \textbf{75} mins to \textbf{28} mins.}
\resumeItem{Implemented the backend for an end-user facing application using \textbf{Python}, \textbf{Node.js}, and \textbf{PostgreSQL}, enabling seamless manual patching resulting in a \textbf{50\%} increase in user engagement and a \textbf{30\%} patch reduction time.}
\resumeItem{Built and optimized \textbf{RESTful APIs} with \textbf{Node} and \textbf{Python}, integrating with \textbf{Kafka} topics and streamlining integration with the Tanium platform.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Deloitte Consulting}{July 2019 -- July 2021}
{Software Engineer}{Gilbert, AZ - Remote}
{Google - Full Stack Developer}
\resumeItemListStart
\resumeItem{Engineered and supported a Reference Management platform for Google Cloud Marketing leveraging \textbf{Python}, \textbf{GCP}, and \textbf{Salesforce}, enhancing campaign efficiency and data accessibility.}
\resumeItem{Designed and deployed custom \textbf{APIs} with \textbf{Node.js} and \textbf{Express}, enabling integration with external vendors.}
\resumeItem{Diagnosed and resolved critical issues in distributed systems, reducing downtime by 25\% through proactive debugging and cross-team collaboration.}
\resumeItemListEnd
\resumeSubHeadingListEnd



\resumeSubHeadingListStart
\resumeSubheading
{Caporaso Lab}{April 2018 -- May 2019}
{Software Developer}{Flagstaff, AZ}
{QIIME2 - Software Developer}
\resumeItemListStart
\resumeItem{Developed core plugins for the open-source QIIME2 framework using \textbf{Python}, \textbf{Miniconda}, and \textbf{Django}.}
\resumeItem{Performed statistical analysis and created meaningful visualizations using \textbf{D3}, \textbf{Vega}, \textbf{Pandas}, and \textbf{Numpy}.}
\resumeItem{Utilized \textbf{Jekyll}, \textbf{Sphinx}, \textbf{Travis CI}, \textbf{Git}, and \textbf{Docker} to maintain and improve the QIIME2 framework.}
\resumeItemListEnd
\resumeSubHeadingListEnd


% List your technical skills here
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
 \small{\item{
       \textbf{Languages}{: Golang, Python, TypeScript, SQL, Bash} \\
       \textbf{Frameworks}{: Node.js, Flask, Django, Gin, GraphQL, REST} \\
       \textbf{Cloud \& Infrastructure}{: AWS (EKS, Lambda, ElastiCache, EventBridge, S3), Google Cloud (Apigee, Compute Engine, GKE, Cloud SQL), Kafka, Terraform, Docker, Kubernetes} \\
       \textbf{DevOps \& Monitoring}{: Git/GitHub Actions, GitLab CI/CD, Jenkins, Splunk, Dynatrace, Prometheus, Grafana} \\
       \textbf{Databases}{: PostgreSQL, MongoDB, OpenSearch (Elasticsearch), Redis, DynamoDB}
       }}
\end{itemize}

% List your colleges here
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Northern Arizona University}{Flagstaff, AZ}
{\normalfont Bachelor of Science in Computer Science}{Jan. 2015 -- May 2019}
{}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}